Review of Assigned Readings

### 2017-12-29 documentation/documentation.tex
corrected setup and tweets collection part. Puls, finished draw version of aggregation process

% Language and font encodings
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}

% Specify bibliography package
\usepackage{csquotes}% Recommended
\usepackage[style=apa]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{references.bib}

% Sets page size and margins
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}
\setlength{\parskip}{1em}

% package for formatting and highlighting source code
\usepackage{listings}
\usepackage{color}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{graphicx}
\usepackage{setspace}

% packages for tikz diagrams
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

% styling for tikz diagrams
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=10cm, minimum height=1cm,text centered, text width=10cm, draw=black, fill=gray!10]
\tikzstyle{process} = [rectangle, minimum width=10cm, minimum height=1cm, text centered, text width=10cm, draw=black, fill=orange!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

% Section Title Margins
\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{3.0ex plus 1ex minus .2ex}{0.7ex}
\titlespacing*{\subsection}
{0pt}{1.4ex}{0pt}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3}

\title{Your Title Goes Here}
\author{Your Name Goes Here}

%************************** DOCUMENT_STARTS_HERE **************************
\begin{document}

\begin{titlepage}
	\begin{figure}
	\centering
	\includegraphics[scale=0.32]{logohsg}
	\end{figure}
\centering
\centering
{\scshape\large School of Management, Economics, Law, Social Sciences and International Affairs \par}
\vspace{1.7cm}
{\huge\bfseries The effect of Twitter activity on \\ Bitcoin price\par}
\vspace{1.0cm}
{\Huge\itshape Documentation\par}
\vspace{1.0cm}     
{\Large Software Engineering for Economists \\ (7,610,1.00) \par}
\vspace{1.2cm}
{Alen Stepic - 11-475-258 \\ Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\ Chi Xu - XX-XXX-XXX \par}
\vspace{1.2cm}
Fall Term 2017 \\
\vspace{1.2cm}
{Supervisor\\ Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen\\ Department of Economics\par}
\vspace{0.8cm}
{\centering\today\par}
\end{titlepage}

@@

\tableofcontents

\listoffigures\bigskip 
\section*{List of Abbreviation} 
\begin{acronym}[ASECRETTT]
\acro{API}{Application Programming Interface}
\acro{ATOKEN}{Access Token}
\acro{ASECRET}{Access Token Secret}
\acro{BPI}{Bitcoin Price Index}
\acro{BTC}{Bitcoin}
\acro{CKEY}{Consumer Key}
\acro{CSECRET}{Consumer Secret}
\acro{JSON}{Java Script Object Notation}
\acro{RPI}{Raspberry Pi}
\acro{SSH}{Secure Shell}
\acro{USD}{US Dollar}
\end{acronym}

\begin{spacing}{1.2}
\cleardoublepage\pagenumbering{arabic}

\section{Introduction}
In the academic environment accountability and reproducibility is important. However, the publishing process of papers and journals seem to be outdated as reproducability is not evaluated by many journals. \parencite[p.~888]{mccullough2003} New ways of data collection and data processing exist by using computational economics. The usage of algorithms can increase effectiveness and efficiency. Hence, much lager data sets can be proceeded. However this creates also new problems regarding to traceability and reproducibility. Often cited academic paper exist, where the initial computation is not reproducible \parencite[pp.~874--887]{mccullough2003}. Replicating data or existing results do not provide any new knowledge at all. Nevertheless, the ability to reproduce is key in science and non-reproducable work can not be characterized as science or used as a basis for policy making \parencite[p.~888]{mccullough2003}. This explains why reproduction is of great relevance.

\subsection{Goal of the paper}
The goal of this documentation is the provision of a description. This description should enable the reader to reproduce the results discussed in the separate paper. Thus, it contains an explanation how the input data have been gathered, stored, aggregated and analysed. In other words, the input data, the model core, the model parameters and the applied math program are explained.

\subsection{Methodology}
This documentation consists out of four chapters. The first chapter contains a short introduction and provides the reader with an overview about the topic. Furthermore it points out the relevance of documentation. The second chapter discusses the input data. This includes the process of gathering and storing twitter tweets as well as the gathering of the bitcoin price data. The third chapter discusses how the data is aggregated by pointing out the core model and its parameters. Finally the fifth chapter discusses how the analysis has been conducted.

\subsection{Scope}
The scope of the documentation is the provision of an overview about the different steps which have been conducted to obtain the results in the paper. It does not contain any discussions about the results of the separate paper. It is not a deep description of the code as the code itself as the code is documented separately. Nevertheless, important lines of code are discussed.

\section{Setup}
\subsection{Requirements to run Python scripts}
Before you go any further, make sure that at least Python version 3.0.0 available from your command line. You can check this by running:
\begin{lstlisting}[language=bash]
    python --version
\end{lstlisting}
You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from python.org.\\
On top you need various packages. We created a the requirements file \verb|requirements.txt|, which contains all required packages to run Python scripts of the project. The list of packages to be installed using pip install like so:
\begin{lstlisting}[language=bash]
    pip install -r requirements.txt
\end{lstlisting}
Now you should be ready to run the Python scripts.

@@

\section{Data Collection}
This section contains a detailed description of how the data for the sequential analysis is gathered and stored. This includes two  subsections the (1) tweets data and the (2) bitcoin price data.
\subsection{Tweets Data}
Whit the python script real-time twitter data are streamed and stored. This happens with help of a raspberry pi.
\subsubsection{Python Script}
Twitter offers different Application Programming Interfaces (API) for collecting data. However, the time frame for gathering data on a freely base with full access is limited to 7 days \parencite{twitterinc2017a}. On the other hand, python offers different twitter libraries. Such as the open-source package tweepy. This package has been used for streaming the twitter data as it simplify the script.

@@

After the creation of a application, the keys and tokens can be extracted. Figure \ref{figkeysandtokens} illustrates how to retrieve the keys and tokens.\\
\begin{figure}[H]
\centering
\includegraphics[scale=0.6]{twitteraccess}
\caption{Twitter Keys and Access Tokens, based on \textcite{twitterinc2017c}.}
\label{figkeysandtokens}
\end{figure}

\paragraph{Twitter Streaming API}\mbox{}\\{}
By running the python script \verb|collectTwitterData.py| real-time twitter data is pushed in a Java Script Object Notation (JSON) format. Tweets are just pushed in case a tweet contains the defined key word \verb|bitcoin|.
\begin{lstlisting}[language=bash]
$ python collectTwitterData.py
\end{lstlisting}

From the JSON format the following parameters are decoded:
\begin{itemize}
\item created at: Timestamp of the created tweet
\item text: Text of the tweet
\end{itemize}

The timestamps are in UTC time.

After a successfully decoding the parameters the data is appended to the \verb|twitterData.csv| file in a new row and saved in the folder \verb|/data|.

An excerpt of an example response looks like the following:
\begin{lstlisting}
[
    {
        "created_at": Tue Dec 19 20:40:48 +0000 2017, 
        "text": "RT @WhiteBitcoin: New Bitcoin White. Effective, Flexible, Reliable", 
    }, 
    {
        "created_at": Tue Dec 19 20:40:49 +0000 2017 ,
        "text": "As #bitcoin prices surge, #xrp remains affordable and FAST!",
    }, 
    {
        "created_at": Tue Dec 19 20:40:49 +0000 2017, 
        "text": "Singapore issues bitcoin warning after price rise - #BTC #Bitcoin #Crypto", 
    }
]
\end{lstlisting}

Furthermore to ensure a high quality data set an exception has been integrated into the \verb|collectTwitterData.py| script. If an error occurs an email will be sent with the error message. Furthermore the logfile will be  appended to \verb|/data/tweet_collection_error_log.csv|.

\subsubsection{Hardware Setup}
As explained in the previous section the twitter API was used to filter tweets in real time based on the buzzword \"bitcoin\". The Python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection. This approach allowed us to ensure a continuous data stream while being able to access the program output regardless of time and location. Furthermore, due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server. The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\\

\begin{enumerate}

\item Setup of the Raspberry Pi
\begin{enumerate}
\item Burn image 2017-11-29-raspbian-stretch.zip to micro SD card available from
\begin{lstlisting}[language=bash]
https://www.raspberrypi.org/downloads/raspbian/
\end{lstlisting}
\item Boot image from micro SD card 
\item Open SSH session using PuTTY SSH client for Windows available from
\begin{lstlisting}[language=bash] 
https://www.chiark.greenend.org.uk/~sgtatham/putty/latest.html
\end{lstlisting}
\item Login to server with credentials 
\end{enumerate}

@@

\item Download the collected data
\begin{enumerate}
\item Install FileZilla available from
\begin{lstlisting}[language=bash] 
https://filezilla-project.org/
\end{lstlisting}
\item Connect to rpi and navigate to data location \newline
\item Download data manually \newline \newline \end{enumerate}
\end{enumerate}

In summary, this approach worked well and ran smoothly. A clean setup is recommended to ensure a continuous data stream over a longer period.

@@

\subsubsection{API: Bitcoinaverage.com}
Bitcoinaverage.com offers a free API that provides real-time and historical price data for a range of crypto-currencies including Bitcoin. The following requests delivers data for an per hour monthly sliding window.

\paragraph{Request}\mbox{}\\
The request to get the data for an per hour monthly sliding window looks as follows. This request require authentication that requires registration and the generation of an API key. The registration and generation of an API key is freely available on bitcoinaverage.com. The collectCryptocurrencyData.py already contains the necessary keys. This means that you need no register or generate keys to execute the script collectCryptocurrencyData.py.  
\begin{lstlisting}[language=bash]
https://apiv2.bitcoinaverage.com/indices/global/history/BTCUSD?period=monthly&?format=json
\end{lstlisting}

\paragraph{Response}
An excerpt of an example response looks like the following:
\begin{lstlisting}
[
    {
        "high": 8271.04, 
        "average": 8247.83, 
        "open": 8242.39,
        "low": 8217.72, 
        "time": "2017-11-22 15:00:00"
    }, 
    {
        "high": 8246.82,
        "average": 8203.19,
        "open": 8203.81,
        "low": 8157.25,
        "time": "2017-11-22 14:00:00"
    }, 
    {
        "high": 8267.27, 
        "average": 8238.62, 
        "open": 8248.77, 
        "low": 8198.54, 
        "time": "2017-11-22 13:00:00"
    }
]
\end{lstlisting}

@@

Here a short description of what happens at the various steps:
\linebreak\linebreak
\textbf{Load BPI data set} The script takes the BPI data set that is located at \verb|data/bpi.csv|.
\linebreak\linebreak
\textbf{Calculate first differences for BPI data} The first differences of the BPI closing prices and the natural logarithm of the first differences of the BPI closing prices are calculated. The reason for calculating these values is given in the data analysis section.
\linebreak\linebreak
\textbf{Load tweets data set} The script takes the tweets data set that is located at \verb|data/twitterData.csv|.
\linebreak\linebreak
\textbf{Count number of tweets on an hourly basis} First, groups the tweets by hour. Second, counts the number of tweets for every hour.
\linebreak\linebreak
\textbf{Calculate first differences for number of tweets on an hourly basis} The first differences of the number of tweets and the natural logarithm of the first differences of the number of tweets are calculated. Again, the reason for calculating these values is given in the data analysis section.
\linebreak\linebreak
\textbf{Merge number of tweets with BPI data (incl. first differences)} 
Insert Image
\linebreak\linebreak
\textbf{Generate and save CSV file} Finally, a CSV file is generated with the merged data.

>>>>

%% Language and font encodings
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}

% Specify bibliography package
\usepackage{csquotes}% Recommended
\usepackage[style=apa]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

\addbibresource{references.bib}

%% Sets page size and margins
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}
\setlength{\parskip}{1em}

%% package for formatting and highlighting source code
\usepackage{listings}
\usepackage{color}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{graphicx}
\usepackage{setspace}

%% packages for tikz diagrams
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

%% styling for tikz diagrams
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=10cm, minimum height=1cm,text centered, text width=10cm, draw=black, fill=gray!10]
\tikzstyle{process} = [rectangle, minimum width=10cm, minimum height=1cm, text centered, text width=10cm, draw=black, fill=orange!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

% Section Title Margins
\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{3.0ex plus 1ex minus .2ex}{0.7ex}
\titlespacing*{\subsection}
{0pt}{1.4ex}{0pt}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\title{Review of Assigned Readings}
\author{Your Name Goes Here}

    \begin{document}
    \begin{titlepage}
      	\begin{figure}
      	\centering
        \includegraphics[scale=0.35]{logohsg}
        \end{figure}
        \centering
        School of Management, Economics, Law, Social Schiences and International Affairs \par
        \vspace{2.5cm}
        {\huge\bfseries The effect of Twitter activity on
Bitcoin price\par}      
        {\Huge\itshape Documentation\par}
        \vspace{1.5cm}     
        {Software Engineering for Economists \\ (7,610,1.00) \par}
        \vspace{1.3cm}
        {Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\
       	Alen Stepic - 11-475-258 \\Chi Xu - XX-XXX-XXX \par}
        \vspace{1cm}
        Fall Term 2017
        \vfill
        Supervisor
        \linebreak
        Prof. Dr. Philipp \textsc{Zahn}
        \linebreak
        Department of Economics

    % Bottom of the page
     {\centering \today\par}

    \end{titlepage}

    \clearpage
    \tableofcontents

@@

    \listoffigures\bigskip 
    \section*{List of Abbreviation} 
	\begin{acronym}[ASECRETTT] 
	\acro{API}{Application Programming Interface}
	\acro{ATOKEN}{Access Token}
	\acro{ASECRET}{Access Token Secret}
	\acro{BPI}{Bitcoin Price Index}
	\acro{BTC}{Bitcoin}
	\acro{CKEY}{Consumer Key}
	\acro{CSECRET}{Consumer Secret}
	\acro{JSON}{Java Script Object Notation}
	\acro{RPI}{Raspberry Pi}
	\acro{SSH}{Secure Shell}
	\acro{USD}{US Dollar}
	\end{acronym}
    \clearpage

\begin{spacing}{1.2}
\cleardoublepage\pagenumbering{arabic}
\section{Introduction}
In the academic environment accountability and reproducibility is important. However, the publishing process of papers and journals seem to be outdated as reproducability is not evaluated by many journals. \parencite[p.~888]{mccullough2003} New ways of data collection and data processing exist by using computational economics. The usage of algorithms can increase effectiveness and efficiency. Hence, much larger data sets can be proceeded. However, this creates also new challenges regarding traceability and reproducibility. Often cited academic paper exist, where the initial computation is not reproducible \parencite[pp.~874--887]{mccullough2003}. Replicating data or existing results do not provide any new knowledge at all. Nevertheless, the ability to reproduce is key in science, and non-reproducible work can not be characterized as science or used as a basis for policy-making \parencite[p.~888]{mccullough2003}. This explains why reproduction is of great relevance.

\subsection{Goal of the paper}
The goal of this documentation is the provision of a description. This description should enable the reader to reproduce the results discussed in the separate (Comment Joel: suggesting-> accompanying paper ) paper. Thus, it contains an explanation how the input data have been gathered, stored, aggregated and analysed. In other words, the input data, the model core, the model parameters and the applied math program are explained.

\subsection{Methodology}
This documentation consists out of four chapters. The first chapter contains a short introduction and provides the reader with an overview of the topic. Furthermore, it points out the relevance of documentation. The second chapter discusses the input data. This includes the process of gathering and storing twitter tweets as well as the gathering of the bitcoin price data. The third chapter discusses how the data is aggregated by pointing out the core model and its parameters. Finally, the fifth chapter explains how the analysis has been conducted.

\subsection{Scope}
The scope of the documentation is the provision of an overview of the different steps which have been conducted to obtain the results in the paper. It does not contain any discussions about the results of the separate paper (Comment Joel: suggesting-> accompanying paper ). It is not a deep description of the code as the code itself as the code is documented separately. Nevertheless, important lines of code are discussed. 
\clearpage

\section{Setup}
This section goes through the setup that you need for exectuing the code that is discussed in this documentation.
\subsection{Github Repository}
All code is available on the following github repository:
\newline
\verb|https://github.com/joelsonderegger/twitterbitcoin/|
\subsection{Requirements to run Python scripts}
Before you go any further, make sure that at least Python version 3.0.0 is available from your command line. You can check this by running in your command line:
\begin{lstlisting}[language=bash]
    python --version
\end{lstlisting}
You should get some output like Python 3.7.13. If you do not have at least Python version 3.0.0, please install the latest 3.x version from python.org.
\newline \newline
On top you need various Python packages. We created a  requirements file \verb|requirements.txt|, which contains all required packages to run the Python scripts of this project. You can find the  \verb|requirements.txt| in the root directory of our github repository. The list of packages can be installed using pip install like so:
\begin{lstlisting}[language=bash]
    pip install -r requirements.txt
\end{lstlisting}
Now you should be ready to run the Python scripts.

@@

\section{Data Collection}
This section contains a detailed description of how the data for the sequential analysis is gathered and stored. Two separate data sets will be collected: (1) Tweets data and  (2) Bitcoin price index data.
\subsection{Tweets Data}
Whit the Python script real-time Twitter data are streamed and stored. This happens with help of a Raspberry Pi.
\subsubsection{Python Script}
Twitter offers different Application Programming Interfaces (API) for collecting data. However, the time frame for gathering data on a freely base with full access is limited to 7 days \parencite{twitterinc2017a}. On the other hand, Python offers different twitter libraries. Such as the open-source package tweepy. This package has been used for streaming the twitter data as it simplify the script.

(Comment Joel: I think we need a short paragraph about tweepy here. What is tweepy?)

@@

After the creation of a application, the keys and tokens can be extracted. Figure \ref{figkeysandtokens} illustrates how to retrieve the keys and tokens.
\begin{figure}[H]
\centering
	\includegraphics[scale=0.6]{twitteraccess}
\caption{Twitter Keys and Access Tokens, based on \textcite{twitterinc2017c}.}
	\label{figkeysandtokens}
\end{figure}

\paragraph{Running the Python Scrupt}\mbox{}\\{}
By running the Python script \verb|collectTwitterData.py| real-time twitter data is gathered on an ongoing basis until you stop the script forcefully.
\begin{lstlisting}[language=bash]
    $ python collectTwitterData.py
    \end{lstlisting}

The Tweepy API provides the tweets data in a Java Script Object Notation (JSON) format. Tweets are only received in case a tweet contains the predefined key word \verb|bitcoin|. While a single tweet consists of many attributes we are only interested in two attributes:
\begin{itemize}
    \item created\_at: Timestamp of the created tweet (in UTC time)
    \item text: Text of the tweet
\end{itemize}

An example for a response from the Tweepy API looks like this (of course this shows only the two attributes we are interested in):
\begin{lstlisting}
    {
        "created_at": Tue Dec 19 20:40:49 +0000 2017, 
        "text": "Singapore issues bitcoin warning after price rise - #BTC #Bitcoin #Crypto", 
    }
\end{lstlisting}

The \verb|text| attribute needs to be encoded from the raw JSON format into the UTF-8 format for further analysis. After successfully encoding the \verb|text| attribute a tweet is appended to the \verb|twitterData.csv| file as a new row and saved in the fo

Furthermore, to ensure a high quality data set it needs to be complete without missing any data points for the observed period. Thus, we have built in an exception handler into the \verb|collectTwitterData.py| script. If an error occurs an email will be sent with the error message. Additionaly, any exception that occurs during the exectuing of the script will be added to the log file \verb|/data/tweet_collection_error_log.csv|.

\subsubsection{Hardware Setup}
As explained in the previous section the twitter API was used to filter tweets in real time based on the buzzword \"bitcoin\". The Python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection. This approach allowed us to ensure a continuous data stream while being able to access the program output regardless of time and location. Furthermore, due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server. The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\newline

\begin{enumerate}
\item Setup of the Raspberry Pi
\begin{enumerate}
\item Burn image 2017-11-29-raspbian-stretch.zip to micro SD card available from
\begin{lstlisting}[language=bash]
https://www.raspberrypi.org/downloads/raspbian/
\end{lstlisting}
\item Boot image from micro SD card 
\item Open SSH session using PuTTY SSH client for Windows available from
\begin{lstlisting}[language=bash] 
https://www.chiark.greenend.org.uk/~sgtatham/putty/latest.html
\end{lstlisting}
\item Login to server with credentials 
\end{enumerate}

@@

\item Download the collected data
\begin{enumerate}
\item Install FileZilla available from
\begin{lstlisting}[language=bash] 
https://filezilla-project.org/
\end{lstlisting}
\item Connect to rpi and navigate to data location \newline
\item Download data manually \newline \newline \end{enumerate}
\end{enumerate}
In summary, this approach worked well and ran smoothly. A clean setup is recommended to ensure a continuous data stream over a longer period.

@@

\subsubsection{API: Bitcoinaverage.com}
Bitcoinaverage.com offers a free API that provides real-time and historical price data for a range of crypto-currencies including Bitcoin. The following requests delivers data for an per hour monthly sliding window.
\paragraph{Request}\mbox{}\\
The request to get the data for an per hour monthly sliding window looks as follows. This request require authentication that requires registration and the generation of an API key. The registration and generation of an API key is freely available on bitcoinaverage.com. The collectCryptocurrencyData.py already contains the necessary keys. This means that you need no register or generate keys to execute the script collectCryptocurrencyData.py.  
\begin{lstlisting}[language=bash]
https://apiv2.bitcoinaverage.com/indices/global/history/BTCUSD?period=monthly&?format=json
\end{lstlisting}
\paragraph{Response}
An excerpt of an example response looks like the following:
\begin{lstlisting}
[
    {
        "high": 8271.04, 
        "average": 8247.83, 
        "open": 8242.39,
        "low": 8217.72, 
        "time": "2017-11-22 15:00:00"
    }, 
    {
        "high": 8246.82,
        "average": 8203.19,
        "open": 8203.81,
        "low": 8157.25,
        "time": "2017-11-22 14:00:00"
    }, 
    {
        "high": 8267.27, 
        "average": 8238.62, 
        "open": 8248.77, 
        "low": 8198.54, 
        "time": "2017-11-22 13:00:00"
    }
]
\end{lstlisting}

@@

Here a short description of what happens at the various steps: 
\paragraph{Load BPI data set}\mbox{}\\
The script takes the BPI data set that is located at \verb|data/bpi.csv|.

\paragraph{Calculate first differences for BPI data}\mbox{}\\
The first differences of the BPI closing prices and the natural logarithm of the first differences of the BPI closing prices are calculated. The reason for calculating these values is given in the data analysis section.

\paragraph{Load tweets data set}\mbox{}\\ 
The script takes the tweets data set that is located at \verb|data/twitterData.csv|.

\paragraph{Count number of tweets on an hourly basis}\mbox{}\\ F
irst, groups the tweets by hour. Second, counts the number of tweets for every hour.

\paragraph{Calculate first differences for number of tweets on an hourly basis}\mbox{}\\ 
The first differences of the number of tweets and the natural logarithm of the first differences of the number of tweets are calculated. Again, the reason for calculating these values is given in the data analysis section.

\paragraph{Merge number of tweets with BPI data (incl. first differences)}\mbox{}\\
Up to this point there are the two seperate data frames df\_tweets\_per\_hour and df\_bpi.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.52]{dfseperate.png}
\end{figure}
By using the \verb|pandas.DataFrame.join| function the columns of the  \verb|df_tweets_per_hour| are joined with  \verb|df_bpi| on the  \verb|MultiIndex(Y, M, D, H)|. The code snipped looks as following\:
\begin{lstlisting}[language=bash]
...
df_merged = df_tweets_per_hour.join(df_bpi, how='left')
...
\end{lstlisting}
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.52]{dfmerged.png}
\end{figure}

\paragraph{Generate and save CSV file}\mbox{}\\ Finally, a CSV file is generated with the merged data.
